### 2015-04-09 results.tex
Adding filter design section

\subsection{Cartesian Lattice}
Blurb about cartesian lattices.

\subsubsection{Basis function}
Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a triliniear piecewise polynomial. It is easy to see, by definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions. Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ \Xii_{C2} \ \Xii_{C2} \right]}$. A box spline is easily centered by taking $M_\mathbf{\Xii}(\vx + \mathbf{c_\Xii})$, with $\mathbf{c_\Xii}:=\sum_{\xi \in \mathbf{\Xii}} \frac{1}{2}\xi$. We will assume, unless otherwise stated, that $M_\mathbf{\Xii}$ defines the centered box spline generated by $\mathbf{\Xii}$. Due to the smoothness requirements of the optimization constraint, we only considered the spline $M_{\Xii_{C4}}$.

\subsubsection{Filter weights}
This is where we derive filter weights for the experiments.

\subsection{BCC Lattice}
Blurb about cartesian lattices.

\subsubsection{Basis function}
On the BCC lattice, a choice of {\footnotesize
\begin{equation*}
	\mathbf{\Xii_{B}} := 
	\begin{bmatrix} 
		-1 & 1 & 1 & -1 \\
		1 & -1 & 1 & -1 \\
		1 & 1 & -1 & -1 
	\end{bmatrix}
\end{equation*}}

@@

\subsubsection{Filter weights}

>>>>

\subsection{Cartesian Lattice}
\subsubsection{Basis function}
Choosing $\mathbf{\Xii = \Xii_{C2} := \left[ I_3  \ I_3 \right]}$ (the $3 \times 6$ matrix created by the union of two identity matrices) generates a triliniear piecewise polynomial. It is easy to see, by definition, when $\mathbf{\Xii_{C2}}$ is used in conjunction with \EQp{eq:box_def}, the resulting function $M_\mathbf{\Xii_{C2}}(\vx)$ corresponds to the non-centered tensor product extension of the linear B-spline in three dimensions. Likewise, the non-centered cubic tensor product box spline is given by $M_\mathbf{\Xii_{C4}}(\vx)$, where $\mathbf{\Xii_{C4} := \left[ \Xii_{C2} \ \Xii_{C2} \right]}$. A box spline is easily centered by taking $M_\mathbf{\Xii}(\vx + \mathbf{c_\Xii})$, with $\mathbf{c_\Xii}:=\sum_{\xi \in \mathbf{\Xii}} \frac{1}{2}\xi$. We will assume, unless otherwise stated, that $M_\mathbf{\Xii}$ defines the centered box spline generated by $\mathbf{\Xii}$. Due to the smoothness requirements of the optimization constraint, we only considered the spline $M_{\Xii_{C4}}$.

\subsubsection{Filter Design}
Extending the filter in table 1

\subsection{BCC Lattice}
\subsubsection{Basis function}
On the BCC lattice, a choice of {\footnotesize
\begin{equation*}
	\mathbf{\Xii_{B}} := 
	\begin{bmatrix} 
		-1 & 1 & 1 & -1 \\
		1 & -1 & 1 & -1 \\
		1 & 1 & -1 & -1 
	\end{bmatrix}
\end{equation*}}

@@

\subsubsection{Filter Design}
\label{sec:poissonFilterDesign}

We now turn to the problem of designing filters that discretize the operator
$\ftpairs{\invlaplacian}{(-4\pi^2(\omega_1^2 +
  \omega_2^2))^{-1}}$, and
are to be used in conjunction with the tensor-product B-splines. Recall that the
space $\aspace{\ints^2_h}{\tpbs^k}$ generated by $\tpbs^k(x_1,x_2) =
\cbs^{k}(x_1)\cbs^{k}(x_2)$ (where $\cbs^k$ is as defined
in~\EQ{eq:1DBspline}), satisfies the approximation property:
$\order{\ints^2}{\tpbs^k}=k+1$. This result also extends to the Cartesian lattice in
higher dimensions. Consequently, we cover the 2D case in detail here. The
extension to 3D is left to the reader.

\paragraph{Interpolation}
For the generator $\tpbs^k$, we are interested in a $(k+1)$-th order
asymptotically optimal discretization of the inverse Laplacian
$\invlaplacian$. According to Proposition~\ref{prop:1}, we need the
two filters $p_{\tpbs^k}$ and $\lambda$.

Since $\tpbs^k$ is a compact generator, $p_{\tpbs^k}$ will also be a compact
filter. Furthermore, since $\tpbs^k$ is separable, $p_{\tpbs^k}$ can be
determined by sampling $\cbs^k(x)$ to yield the filter $p_{\cbs^k}[n] =
\cbs^k(n)$ where $n \in \ints$. The weights of $p_{\tpbs^k}$ are then obtained
by a simple tensor product, i.e. $p_{\tpbs^k}[n_1,n_2] =
p_{\cbs^k}[n_1]p_{\cbs^k}[n_2] \ftpairs{}{} \ft{P}_{\tpbs^k}(\omega_1,\omega_2)
= \ft{P}_{\cbs^k}(\omega_1)\ft{P}_{\cbs^k}(\omega_2)$.

As for the filter $\lambda$ that discretizes $\laplacian$, we follow a
similar approach and first look for a symmetric and compact 1D filter
$\lambda_1$ that satisfies the 1D analog of~\eqref{eq:opCriterionHomo},
i.e. $\ft{\Lambda}_1(\omega) = -4\pi^2\omega^2 + O(\omega^{k+3})$. The
unknown filter weights are determined by requiring that the Taylor
developments of $(\ft{\Lambda}_1(\omega) + 4\pi^2\omega^2)$ be zero up to
$\omega^{k+3}$. The filter $\ftpairs{\lambda}{\ft{\Lambda}}$ is then given by a
simple addition, i.e. $\ft{\Lambda}(\omega_1,\omega_2) =
\ft{\Lambda}_1(\omega_1) + \ft{\Lambda}_1(\omega_2)$.

The sizes of $p_{\cbs^k}$ and $\lambda_1$ obviously depend on the degree
$k$. The filters used in our experiments are tabulated in
Table~\ref{tab:filters}.

\begin{table*}[t!]
  \footnotesize
  \caption[Poisson filters for the Cartesian lattice]{The various 1D filters to
  be used in conjunction with bilinear and bicubic approximation.}
  \label{tab:filters}
  \centering
  \begin{tabular}{cc|cc}
    \toprule
     & $\aspace{\ints^2_h}{\tpbs^1}$ & \multicolumn{2}{c}{$\aspace{\ints^2_h}{\tpbs^3}$}\\
     & Interp. & Interp. & Quasi. ($l=5$)\\
    \midrule
    $p_{\cbs^k}[n]$ & $\delta_n$ & $[\tfrac{1}{6}\; \tfrac{2}{3}\; \tfrac{1}{6}]$& $[\tfrac{1}{120}\; \tfrac{13}{60}\; \tfrac{11}{20}\; \tfrac{13}{60}\; \tfrac{1}{120}]$\\
    $\ft{P}_{\cbs^k}(\tfrac{\nu}{2\pi})$ & $1$ & $\tfrac{1}{3}(2 + \cos(\nu))$&
    $\tfrac{1}{60}(33+26\cos(\nu) + \cos(2\nu))$\\
    \midrule
    $\lambda_1[n]$ & $[1\; {-2}\; 1]$ & $[\tfrac{-1}{12}\; \tfrac{4}{3}\;
    \tfrac{-5}{2}\; \tfrac{4}{3}\; \tfrac{-1}{12}]$& $[\tfrac{1}{90}\; \tfrac{-3}{20}\; \tfrac{3}{2}\; \tfrac{-49}{18}\; \tfrac{3}{2}\; \tfrac{-3}{20}\; \tfrac{1}{90}]$\\
    $\ft{\Lambda}_1(\tfrac{\nu}{2\pi})$ & $-2 + 2\cos(\nu)$&
    $\tfrac{2}{3}(-7+\cos(\nu))\sin^2(\tfrac{\nu}{2})$& $\tfrac{2}{45}(-111 + 23\cos(\nu) - 2\cos(2\nu))\sin^2(\tfrac{\nu}{2})$\\
    \midrule
    $w_1[n]$ & & & $[\tfrac{1}{362880}\; \tfrac{251}{181440}\;
    \tfrac{913}{22680}\; \tfrac{44117}{181440}\; \tfrac{15619}{36288}\; \cdots]$\\
    $\ft{W}_1(\tfrac{\nu}{2\pi})$ & &
    \multicolumn{2}{r}{$\scriptscriptstyle{\tfrac{1}{181440}(78095 + 88234\cos(\nu) + 14608\cos(2\nu) + 502\cos(3\nu)+ \cos(4\nu))}$}\\
    & & & \\
    $a_{\cbs^k}[n]$ & & & $[\tfrac{1}{5040}\; \tfrac{1}{42}\;
    \tfrac{397}{1680}\; \tfrac{151}{315}\; \tfrac{397}{1680}\; \tfrac{1}{42}\; \tfrac{1}{5040}]$\\
    $\ft{A}_{\cbs^k}(\tfrac{\nu}{2\pi})$ & & & $\scriptscriptstyle{\tfrac{1}{2520}(1208 + 1191\cos(\nu) + 120\cos(2\nu) + \cos(3\nu))}$\\
    \bottomrule
  \end{tabular}
\end{table*}

\paragraph{Quasi-Interpolation}
For the quasi-interpolative model, we need the additional filter
$q$~\eqref{eq:quasiWeights}. Choosing $\psi$ to be the tensor product
B-spline $\tpbs^l$ where $l>k$, the weights of $q$ are given by the
tensor product of the 1D filter $q_1[n] := (\cbs^l \ast
\dual{\cbs}^k)(n)$ with itself. Using the recursive definition
of the 1D B-splines, $q_1$ can be further split as $q_1[n]
= (w_1 \ast a_{\cbs^k}^{-1})[n]$ where $w_1[n] := \cbs^{k+l+1}(n)$ and
$\ftpairs{a_{\cbs^k}^{-1}[\cdot]}{\tfrac{1}{\ft{A}_{\cbs^k}(\cdot)}}$. Example
filter weights for the case $l=5$ are provided in Table~\ref{tab:filters}.

\subsubsection{BCC Lattice}
It is convenient to introduce a scaled version of the BCC lattice
$\lattice{H}$ generated by the matrix $\mat{H} =
\sqrt[3]{4}\mat{B}$. With respect to $\lattice{H}$, we denote the
order-$k$ ($k \in 2\ints_+$) rhombic-dodecahedral box spline as
$\bccbs{k}(\vect{x}) :=
\boxsp[k/2]{\mat{\Theta}}(\vect{x}/\sqrt[3]{4})$. Note that $k$ now
refers to the approximation order of the box-spline rather than its
polynomial degree.

\paragraph{Interpolation}
The operator we wish to discretize is
$\ftpairs{\invlaplacian}{-4\pi^2(\omega_1^2 + \omega_2^2 + \omega_3^2)^{-1}}$.
According to~Proposition~\ref{prop:1}, we need the combined filter
$(p_{\bccbs{k}} \ast \lambda)$ where $\ftpairs{\lambda}{\ft{\Lambda}}$
satisfies~\eqref{eq:discreteLaplacian}, i.e. $\ft{\Lambda}(\vect{\omega}) =
-4\pi^2\norm{\vect{\omega}}^2 + O(\norm{\vect{\omega}}^{k+2})$. The compact
filter $p_{\bccbs{k}}$ is non-separable and is determined by the samples of
$\bccbs{k}$, i.e.
$p_{\bccbs{k}}[\vect{x}_j] = \bccbs{k}(\vect{x}_j)$ where $\vect{x}_j \in
\lattice{H}$.

As for the filter $\lambda$, observe that
\begin{equation}
  \norm{\vect{\omega}}^2 = \frac{1}{4}\sum_{i=1}^4
  (\vect{\theta}_i \cdot \vect{\omega})^2,
\end{equation}
where the (scaled) box spline direction vectors $\vect{\theta}_i$ ($i
\in \{1,2,3,4\}$) correspond to the column vectors
$\transp{(1,1,-1)}$, $\transp{(1,-1,1)}$, $\transp{(-1,1,1)}$ and
$\transp{(-1,-1,-1)}$ respectively. Since $\vect{\theta}_i \in
\lattice{H}$, we can re-use the 1D filter $\lambda_1[n]$ from the
previous section and apply it across the directions $\vect{\theta}_i$
to yield the filter $\lambda$.  Therefore,
$\ftpairs{\lambda}{\ft{\Lambda}}$ is given by
\begin{equation}
  \ft{\Lambda}(\vect{\omega}) = \frac{1}{4}\sum_{i=1}^4
  \ft{\Lambda}_1(\vect{\theta}_i \cdot \vect{\omega}),
\end{equation}
where the 1D filter $\ftpairs{\lambda_1}{\ft{\Lambda}_1}$ satisfies 
$\ft{\Lambda}_1(\omega) = -4\pi^2\omega^2 + O(\omega^{k+2})$.

Table~\ref{tab:filtersBCC} summarizes the various filters that are the
BCC analogs of Cartesian filters listed in Table~\ref{tab:filters}.

\begin{table*}[t]
  \let\oldcos\cos	
  \renewcommand\cos{\operatorname{c}}
  \footnotesize
  \caption[Poisson filters for the BCC lattice]{Filters to be used in
  conjunction with the linear and quintic box splines on the BCC lattice.
  $\cos(\theta)$ is short for $\oldcos(\theta)$.}
  \label{tab:filtersBCC}
  \centering
  \begin{tabular}{lc|>{\raggedright}p{0.2\textwidth} p{0.4\textwidth}}
    \toprule
     & $\aspace{\lattice{H}_h}{\bccbs{2}}$ &
     \multicolumn{2}{c}{$\aspace{\lattice{H}_h}{\bccbs{4}}$}\\
     & Interp. & Interp. & Quasi. ($l=6$)\\
    \midrule
    $p_{\bccbs{k}}[\vect{y}]$ ($\vect{y} \in \lattice{H}$) & $\delta_{\vect{y}}$
    & $\begin{cases}
    	\tfrac{2}{5} & \text{if $\vect{y} = \vect{0}$},\\
    	\tfrac{1}{20} & \text{if $\norm{\vect{y}} = \sqrt{3}$}, \\
    	\tfrac{1}{30} & \text{if $\norm{\vect{y}} = 2$}, \\
    	0 & \text{otherwise}
    \end{cases}$
    &
    $\begin{cases}
    \tfrac{379}{1680} & \text{if $\vect{y} = \vect{0}$},\\
    	\tfrac{1177}{20160} & \text{if $\norm{\vect{y}} = \sqrt{3}$}, \\
    	\tfrac{7}{180} & \text{if $\norm{\vect{y}} = 2$}, \\
    	\tfrac{43}{10080} & \text{if $\norm{\vect{y}} = \sqrt{8}$},\\
    	\tfrac{17}{20160} & \text{if $\norm{\vect{y}} = \sqrt{11}$},\\
    	\tfrac{1}{4032} & \text{if $\norm{\vect{y}} = \sqrt{12}$},\\
    	\tfrac{1}{10080} & \text{if $\norm{\vect{y}} = 4$},\\
    	0 & \text{otherwise}
    \end{cases}$ 
    \\
    $\ft{P}_{\bccbs{k}}(\tfrac{u}{2\pi},\tfrac{v}{2\pi},\tfrac{w}{2\pi})$
    & $1$ & 
    $\tfrac{1}{15}\bigl(6 + \cos(2u)+\cos(2v)+\cos(2w)$ 
    $+ 6\cos(u)\cos(v)\cos(w) \bigr)$
    &
    $\tfrac{1}{5040}\Bigl(
    2 \cos (u) \cos (v) \cos (w) \bigl[34 \cos (2 u)+34 \cos (2 v)+1143\bigr]$
    $+2 \cos (2w) \bigl[\cos (2 u) \bigl( 5 \cos (2 v)+43\bigr)+43 \cos (2
    v)+196\bigr]$ 
    $+34 \cos(u) \cos (v) \cos (3 w)+43 \cos \bigl(2 (u-v) \bigr)+43 \cos
    \bigl(2 (u+v)\bigr)$
    $+392\cos (2 u)+\cos (4 u)+392 \cos (2 v)+\cos (4
    v)+\cos (4 w)+1137 \Bigr)$
    \\
    \midrule
    $\lambda_1[n]$ & \multicolumn{3}{c}{see Table~\ref{tab:filters}} \\
    $\ft{\Lambda}_1(\tfrac{\nu}{2\pi})$ & \multicolumn{3}{c}{} \\
    \midrule
    $w_{\mathsf{b}}[\vect{y}]$ & N/A & N/A & see
    supplementary material
    \\
    $\ft{W}_{\mathsf{b}}(\vect{\omega})$ & & &  \\
    $a_{\bccbs{k}}[\vect{y}]$ & N/A & N/A & see
    supplementary material
    \\
    $\ft{A}_{\bccbs{k}}(\vect{\omega})$ & & &\\
    \bottomrule
  \end{tabular}
  \let\cos\oldcos
\end{table*}
